Supplememtary examples for:

### 2020-07-22 extensions.Rmd
Made some major revisions to the text

The following discusses several opportunities to extend the basic FE model outlined in the main article, and provides concrete guidance on the implementation in `lavaan`. First, I go over a number of possibilities to relax assumptions associated with the traditional FE model. Then, I discuss the issue of measurement error and show how we can use latent variables to deal with it and properly estimate the coefficients of interest. Then, I show a type of hybrid FE/RE model that allows us to control for time-invariant unobserved heterogeneity while including time-invariant predictors in the model.

>>>>

The following goes into some more detail on the comparison of traditional FE and FE-SEM models and discusses several opportunities to extend the basic FE model outlined in the main article, and provides concrete guidance on the implementation in `lavaan`. First, I verify that the FE-SEM model does, in fact, return essentially identical results compared to the more traditional methods. Then, I go over a number of possibilities to relax assumptions associated with the traditional FE model. Then, I discuss the issue of measurement error and show how we can use latent variables to deal with it and properly estimate the coefficients of interest. Then, I show a type of hybrid FE/RE model that allows us to control for time-invariant unobserved heterogeneity while including time-invariant predictors in the model.

## A comparison with non-SEM methods using the simulated data

Just to be sure that the FE-SEM results do, in fact, line up with the more traditional methods outlined in Section 2 of the main article, we can use the long-format data (see [the supplementary materials at](https://github.com/henrik-andersen/FE-SEM)) to run the typical FE model using the `plm` package [@R-plm_a]. By default, the `plm` function assumes the dataframe is structured so that the first two columns correspond to the individual and time indices, see the [documentation](https://cran.r-project.org/web/packages/plm/plm.pdf) or @R-plm_a.

```{r message=FALSE, warning=FALSE, error=FALSE}
library(plm)

# Run the FE model in plm 
fe1 <- plm(y ~ x, 
           effect = "individual", model = "within", 
           data = df)
summary(fe1)
```

From this, we see that the results are, indeed, essentially identical, with $\hat{\beta}_{FE-SEM} =`r round(lavInspect(fe_sem.fit, "list")[6, 14], 3)` \ (`r round(lavInspect(fe_sem.fit, "list")[6, 15], 3)`)$ and $\hat{\beta}_{FE} = `r round(summary(fe1)$coefficients[1, 1], 3)` \ (`r round(summary(fe1)$coefficients[1, 2], 3)`)$.

Other methods of estimating FE models work in the random or mixed effects model framework. For example, we can include the cluster means per individual of the time-varying independent variables, here $x$, in the equation to achieve within estimates [@Mundlak1978; @Chamberlain1980; @Wooldridge2002].

```{r}
# Generate the cluster means for x per id 
clusterMeanx <- aggregate(df$x, by = list(df$id), FUN = mean)
# Rename the columns 
names(clusterMeanx) <- c("id", "xbar")

# Add the cluster means back into df  
df <- merge(df, clusterMeanx, by = "id")
```

Here using the `plm` function in the `random` setup:

```{r}
fe2 <- plm(y ~ x + xbar, 
           effect = "individual", model = "random",
           data = df)
summary(fe2)
```

And here using the `lmer` function of the `lme4` package [@Bates2015] to estimate a mixed model:

```{r message=FALSE, error=FALSE, warning=FALSE}
library(lme4)

# Run the mixed model in lmer with the cluster means for x 
mixed1 <- lmer(y ~ x + xbar + (1 | id), data = df)
summary(mixed1)
```

In both cases, the models return the same estimates as the FE and FE-SEM models. Also, in both the `random` setup using the `plm` function, and the mixed model using the `lmer` function, we get estimates of the variance components, $\hat{\sigma}^{2}_{\alpha}$ and $\hat{\sigma}^{2}_{\varepsilon}$:

```{r}
# Print the variance components for the plm model  
print(ercomp(fe2), 
      digits = 3)

# Print the variance components for the lmer model 
print(VarCorr(mixed1), 
      comp = c("Variance", "Std.Dev"), 
      digits = 3)
```

From this we see both models report the same estimated variance components, $\hat{\sigma}^{2}_{\alpha} = `r round(ercomp(fe2)[[1]][2], 3)`$ and $\hat{\sigma}^{2}_{\varepsilon} = `r round(ercomp(fe2)[[1]][1], 3)`$, telling us that about `r round(ercomp(fe2)[[1]][2]/(ercomp(fe2)[[1]][1] + ercomp(fe2)[[1]][2]), 3)`% of the residual variance is due to the differences between individuals (shown in the `share` column of the `ercomp()` output). This is what is referred to as the intraclass correlation coefficient, or ICC [@Hox2010].
